Results_setup

### 2020-06-22 src/Result_Setup.Rmd
added M4 and M5 to other traits

@@

```{r Female.specific.glm.M4.M5-temp, echo=FALSE, eval=FALSE}
#Change MLH1 to mean_skel

@@

@@

```{r Q2.1COpos_mus.av.full_glm, echo=FALSE}

Q2.glm_mus.av_1COpos_M4 <- glm(mean_1CO.pos.PER ~ subsp * strain, data = (mouse.level.BivData_table  %>% filter(sex == "male") %>% filter(species == "M.musculus") ) )

sum.Q2.glm_mus.av_1COpos_M4  <- summary(Q2.glm_mus.av_1COpos_M4)$coefficients
#summary(Q2.glm_mus.av_1COpos_M1)$coefficients[,4]

#M4.2 (just strain)
Q2.glm_mus.av_1COpos_M4.2 <- glm(norm.first.foci.pos ~ strain, data= mouse.level.BivData_table %>% filter(sex == "male") %>% filter(species == "M.musculus") )
sum.Q2.glm_mus.av_1COpos_M4.2 <- summary(Q2.glm_mus.av_1COpos_M4.2)$coefficients

@@

```{r Q2.IFD.setup, echo=FALSE}

#identify and remove mice with 1 bivalent observation (MSM:  1feb18_MSM_m1)
#some cells just have 1 cell, but the MSM_m is the only with just 1 bivlent

@@

>>>>

M4 and M5 for short bivalent

```{r Female.shortBivalent.M4.M5, echo=FALSE}
#these M4 and M5 could be run for short and Long
Short.biv_mouse_table$subsp <- factor(Short.biv_mouse_table$subsp, ordered = FALSE)
Short.biv_mouse_table$sex <- factor(Short.biv_mouse_table$sex, ordered = FALSE)
Short.biv_mouse_table$strain <- factor(Short.biv_mouse_table$strain, ordered = FALSE)
#mean_SC
#Short.biv_mouse_table

#M4
ShortBiv.female.glm_M4 <- glm(mean_SC ~ subsp * strain, data= (Short.biv_mouse_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "female") ) )
sum.ShortBiv.female.glm_M4 <- summary(ShortBiv.female.glm_M4)
write.xlsx(as.data.frame( sum.ShortBiv.female.glm_M4$coefficients), "ShortBiv.female.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

#M5
ShortBiv.female.glm_M5 <- glm(mean_SC ~ strain, data= (Short.biv_mouse_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "female") ) )
sum.ShortBiv.female.glm_M5 <- summary(ShortBiv.female.glm_M5)
write.xlsx(as.data.frame( sum.ShortBiv.female.glm_M5$coefficients), "ShortBiv.female.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)

```{r male.ShortBiv.M4.M5, echo=FALSE}
#M4
ShortBiv.male.glm_M4 <- glm(mean_SC ~ subsp * strain, data= (Short.biv_mouse_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "male") ) )
sum.ShortBiv.male.glm_M4 <- summary(ShortBiv.male.glm_M4)
write.xlsx(as.data.frame( sum.ShortBiv.male.glm_M4$coefficients), "ShortBiv.male.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

#M5
ShortBiv.male.glm_M5 <- glm(mean_SC ~ strain, data= (Short.biv_mouse_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "male") ) )
sum.ShortBiv.male.glm_M5 <- summary(ShortBiv.male.glm_M5)
write.xlsx(as.data.frame( sum.ShortBiv.male.glm_M5$coefficients), "ShortBiv.male.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)
```

@@

```{r Female.specific.glm.M4.M5-temp, echo=FALSE, eval=TRUE}
#Change MLH1 to mean_skel

@@

totSC.female.glm_M4 <- glm(mean.skel ~ subsp * strain, data= (mouse.total.skel %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "female") ) )

sum.totSC.female.glm_M4 <- summary(totSC.female.glm_M4)

write.xlsx(as.data.frame( sum.totSC.female.glm_M4$coefficients), "totSC.female.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

totalSC.female.glm.M5 <- glm(mean.skel ~ strain, data= (mouse.total.skel %>% filter(subsp != "Cast")  %>% filter(species == "M.musculus")  %>% filter(sex == "female") ) )
sum_totalSC.female.glm.M5 <- summary(totalSC.female.glm.M5)

#write.table(sum_MLH1.female.spc.glm.M5$coefficients, "~./MLH1repo/sum_MLH1.female.spc.glm.M5.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame( sum_totalSC.female.glm.M5$coefficients), "totalSC.female.glm.M5.xlsx", col.names = TRUE, row.names = TRUE)
```

@@

```{r Female.1COpos.M4.M5, echo=FALSE}
#Change MLH1 to mean_skel

#Pos  PER_Foci_1
#cleanCurated_BivData

cleanCurated_BivData$strain <- factor(cleanCurated_BivData$strain, ordered = F)
cleanCurated_BivData$subsp <- factor(cleanCurated_BivData$subsp, ordered = F)

chrm.1CO.pos.female.glm_M4 <- glm(PER_Foci_1 ~ subsp * strain, data= (cleanCurated_BivData %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "female") ) )

sum.chrm.1CO.pos.female.glm_M4 <- summary(chrm.1CO.pos.female.glm_M4)

write.xlsx(as.data.frame( sum.chrm.1CO.pos.female.glm_M4$coefficients), "chrm.1CO.pos.female.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

chrm.1CO.pos.female.glm_M5 <- glm(PER_Foci_1 ~ strain, data= (cleanCurated_BivData %>% filter(subsp != "Cast")  %>% filter(species == "M.musculus")  %>% filter(sex == "female") ) )
sum_chrm.1CO.pos.female.glm_M5 <- summary(chrm.1CO.pos.female.glm_M5)

#write.table(sum_MLH1.female.spc.glm.M5$coefficients, "~./MLH1repo/sum_MLH1.female.spc.glm.M5.csv", sep=",",row.names = TRUE)

write.xlsx(as.data.frame( sum_chrm.1CO.pos.female.glm_M5$coefficients), "chrm.1CO.pos.female.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)
```

```{r Male.Q2.1COpos_male_M4.M5, echo=FALSE}

#norm.first.foci.pos AND mean_1CO.pos.PER  are the same

male_1COpos.glm_M4 <- glm(norm.first.foci.pos ~ subsp * strain, data = (mouse.level.BivData_table  %>% filter(sex == "male") %>% filter(species == "M.musculus")  ) )

sum.male_1COpos.glm_M4  <- summary(male_1COpos.glm_M4)
#summary(Q2.glm_mus.av_1COpos_M1)$coefficients[,4]

write.xlsx(as.data.frame( sum.male_1COpos.glm_M4$coefficients), "male_1COpos.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

#M5 (just strain)
male_1COpos.glm_M5 <- glm(norm.first.foci.pos ~ strain, data= mouse.level.BivData_table %>% filter(sex == "male") %>% filter(species == "M.musculus") )

sum.male_1COpos.glm_M5 <- summary(male_1COpos.glm_M5)

write.xlsx(as.data.frame( sum.male_1COpos.glm_M5$coefficients), "male_1COpos.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)

@@

@@

```{r Female.IFD.M4.M5, echo=FALSE}
#mean_IFD.2CO_ABS
#mouse.level.BivData_table

mouse.level.BivData_table$strain <- factor(mouse.level.BivData_table$strain, ordered = F)
mouse.level.BivData_table$subsp <- factor(mouse.level.BivData_table$subsp, ordered = F)

#RAW IFD
IFD.raw.female.glm_M4 <- glm(mean_IFD.2CO_ABS ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "female") ) )
sum.IFD.raw.female.glm_M4 <- summary(IFD.raw.female.glm_M4)
write.xlsx(as.data.frame( sum.IFD.raw.female.glm_M4$coefficients), "IFD.raw.female.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

IFD.raw.female.glm_M5 <- glm(mean_IFD.2CO_ABS ~ strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast")  %>% filter(species == "M.musculus")  %>% filter(sex == "female") ) )
sum_IFD.raw.female.glm_M5 <- summary(IFD.raw.female.glm_M5)
write.xlsx(as.data.frame( sum_IFD.raw.female.glm_M5$coefficients), "IFD.raw.female.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)

#PER IFD
IFD.PER.female.glm_M4 <- glm(mean_IFD.2CO_PER ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "female") ) )

sum.IFD.PER.female.glm_M4 <- summary(IFD.PER.female.glm_M4)
write.xlsx(as.data.frame( sum.IFD.PER.female.glm_M4$coefficients), "IFD.PER.female.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

IFD.PER.female.glm_M5 <- glm(mean_IFD.2CO_PER ~ strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast")  %>% filter(species == "M.musculus")  %>% filter(sex == "female") ) )
sum_IFD.PER.female.glm_M5 <- summary(IFD.PER.female.glm_M5)

write.xlsx(as.data.frame( sum_IFD.PER.female.glm_M5$coefficients), "IFD.PER.female.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)

```{r Male.Q2.IFD_male_M4.M5, echo=FALSE}

#RAW IFD
IFD.raw.male.glm_M4 <- glm(mean_IFD.2CO_ABS ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "male") ) )
sum.IFD.raw.male.glm_M4 <- summary(IFD.raw.male.glm_M4)
write.xlsx(as.data.frame( sum.IFD.raw.male.glm_M4$coefficients), "IFD.raw.male.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

IFD.raw.male.glm_M5 <- glm(mean_IFD.2CO_ABS ~ strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast")  %>% filter(species == "M.musculus")  %>% filter(sex == "male") ) )
sum_IFD.raw.male.glm_M5 <- summary(IFD.raw.male.glm_M5)
write.xlsx(as.data.frame( sum_IFD.raw.male.glm_M5$coefficients), "IFD.raw.male.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)

#PER IFD
IFD.PER.male.glm_M4 <- glm(mean_IFD.2CO_PER ~ subsp * strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast") %>% filter(species == "M.musculus") %>% filter(sex == "male") ) )
sum.IFD.PER.male.glm_M4 <- summary(IFD.PER.male.glm_M4)
write.xlsx(as.data.frame( sum.IFD.PER.male.glm_M4$coefficients), "IFD.PER.male.glm_M4.xlsx", col.names = TRUE, row.names = TRUE)

IFD.PER.male.glm_M5 <- glm(mean_IFD.2CO_PER ~ strain, data= (mouse.level.BivData_table %>% filter(subsp != "Cast")  %>% filter(species == "M.musculus")  %>% filter(sex == "male") ) )
sum_IFD.PER.male.glm_M5 <- summary(IFD.PER.male.glm_M5)
write.xlsx(as.data.frame( sum_IFD.PER.female.glm_M5$coefficients), "IFD.PER.male.glm_M5.xlsx", col.names = TRUE, row.names = TRUE)
